Integrated farming and global warming mitigation in Brazil

### 2022-07-29 manuscript/manuscript.qmd
Add info to methods diagram and add one section to methods.

  graph [layout = dot, rankdir = TD, nodesep = 1.2, ranksep = 0.12]

@@

@@

@@

>>>>

  graph [layout = dot, rankdir = TD, nodesep = 1, ranksep = 0.13]

@@

  g [label = 'Directed \n literature \n analysis']
  h [label = 'Critical \n reflection']

@@

  g -> h
  f -> h

@@

### Reflection about the role of integrated crop-livestock-forest systems in the agrarian question

ICLF and the agrarian question, a directed reading towards the construction of a narrative reflection. Environmental (e.g. climate change and biodiversity) and social (e.g. social inequality, food insecurity) contexts.
